Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-11-13 analysis/paper/paper.Rmd
Update description of a leaf

In both experiments, two sample areas, sized 1&nbsp;m&nbsp;x&nbsp;1&nbsp;m, per plot were assessed. The total number of tillers per hill and number of tillers with sheath blight (incidence) were measured for nine hills per sample area. Tiller sheath severity was measured for four tillers per hill and six leaves tiller using a disease assessment rating scale for field evaluation developed at IRRI. The scale is an unequally spaced categorical scale where 0 -- no disease; 1 -- trace to 1&nbsp;\% severity; 2 -- 1 to 5&nbsp;\% severity; 3 -- 5 to 15&nbsp;\% severity; 4 -- 15 to 50&nbsp;\% severity; 5 -- 50 to 100&nbsp;\% severity. Severity was considered to be the amount of leaf or sheath tissue covered by sheath blight lesions. Leaves were rated as green (living) having at least XXX&nbsp;\% living tissue or dead, defined as having less than XXX&nbsp;\% living tissue. The same rating methodology was used in both experiments. Five disease assessments were made in the 2015 experiment and four disease assessments were made in the 2016 experiment, respectively.

>>>>

In both experiments, two sample areas, sized 1&nbsp;m&nbsp;x&nbsp;1&nbsp;m, per plot were assessed. The total number of tillers per hill and number of tillers with sheath blight (incidence) were measured for nine hills per sample area. Tiller sheath severity was measured for four tillers per hill and six leaves tiller using a disease assessment rating scale for field evaluation developed at IRRI. The scale is an unequally spaced categorical scale where 0 -- no disease; 1 -- trace to 1&nbsp;\% severity; 2 -- 1 to 5&nbsp;\% severity; 3 -- 5 to 15&nbsp;\% severity; 4 -- 15 to 50&nbsp;\% severity; 5 -- 50 to 100&nbsp;\% severity. Severity was considered to be the amount of leaf or sheath tissue covered by sheath blight lesions. A leaf was considered living if at least 50&nbsp;% of its area was not brown or dark brown due to natural senescence. A leaf that was yellow green or light green due to a disease, such as tungro or nitrogen deficiency was still considered a living leaf. The same rating methodology was used in both experiments. Five disease assessments were made in the 2015 experiment and four disease assessments were made in the 2016 experiment, respectively.
